Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-04-05 tex/conclusion.tex
last sentence

This thesis exhibited problems in the area of machine learning that can only be fully solved with human expertise.
In this context, visual analytics proved to be a powerful tool in assisting humans in performing this task.
Going forward, domain expertise remains an important role of humans in machine learning.

>>>>

This thesis identified problems in the area of machine learning that can only be fully solved with human expertise.
In this context, visual analytics proved to be a powerful tool in assisting humans in performing those tasks.
% Going forward, human expertise remains an important element for humans in machine learning.
